### 2022-12-31 code/1_exclusions/1_exclusionsCN.Rmd
added analysis with cosine distance

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

@@

```{r}
write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
```

>>>>

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

@@

```{r}
df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_M$subject))),
                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_M$subject))), 
                      ppts_after_demog_excl = c(length(unique(df.resp_M$subject))))
```

```{r}
write.csv(df.resp_M, "../../data/responding/dataCN_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataCN_excl_metadata.csv")
```

### 2022-12-31 code/1_exclusions/1_exclusionsUS.Rmd
added analysis with cosine distance

```{r}
write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
```

>>>>

```{r}
df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_E$subject))),
                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_E$subject))), 
                      ppts_after_demog_excl = c(length(unique(df.resp_E$subject))))
```

```{r}
write.csv(df.resp_E, "../../data/responding/dataUS_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataUS_excl_metadata.csv")
```

### 2022-12-31 code/1_exclusions_exploratory/1_exclusionsCN.Rmd
added analysis with cosine distance

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent == 1.0)

>>>>

df.ppts_att_M <- df.resp_M %>%
  filter(stim_type == "attention check") %>%
  mutate(correct_response = strsplit(cue, "选择")) %>%
  mutate(correct_response = sapply(correct_response, "[[", 2)) %>%
  mutate(correct_response = str_replace_all(correct_response, "“", "")) %>%
  mutate(correct_response = str_replace_all(correct_response, "”", "")) %>%
  mutate(pass_att_check = ifelse(responses == correct_response, 1, 0)) %>%
  group_by(subject) %>%
  summarize(pass_att_check_percent = mean(pass_att_check)) %>%
  filter(pass_att_check_percent >= 0.8)

### 2022-12-31 code/1_exclusions_exploratory/1_exclusionsVN.Rmd
added analysis with cosine distance

#have travelled extensively (more than 6 international experiences of 2 days or longer)
df.oversea_exp_V <- df.demog %>%
  filter(demog_question == "overseaexpnum" & demog_response == "Six or more experiences")

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #95
percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
percent_dropped #0.4739 # will not use this criterion

df.resp_V <- df.resp_V %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_vi_speaker_V), 
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V))

length(unique(df.resp_V$subject)) #124
```

```{r}
write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
```

>>>>

#have travelled extensively (more than 6 international experiences of 2 days or longer)
df.oversea_exp_V <- df.demog %>%
  filter(demog_question == "overseaexpnum" & demog_response == "6 lần trở lên")

ppts_oversea_exp_V = unique(df.oversea_exp_V$subject) #20
percent_dropped = length(intersect(ppts_oversea_exp_V, ppts_resp_V)) / length(unique(df.resp_V$subject))
percent_dropped #0.109

df.resp_V <- df.resp_V %>%
  filter(!(subject %in% ppts_non_native_lang_V),
         !(subject %in% ppts_zh_speaker_V),
         !(subject %in% ppts_lived_abroad_V), 
         !(subject %in% ppts_oversea_exp_V))

length(unique(df.resp_V$subject)) #110
```

```{r}
df.demog_metadata <- data.frame(ppts_finished = c(length(unique(df.ppts_finished_V$subject))),
                      ppts_after_att_check_excl = c(length(unique(df.ppts_att_V$subject))), 
                      ppts_after_demog_excl = c(length(unique(df.resp_V$subject))))
```

```{r}
write.csv(df.resp_V, "../../data/responding/dataVN_excl.csv")
write.csv(df.demog_metadata, "../../data/responding/dataVN_excl_metadata.csv")
```

### 2022-12-31 code/2_combine/2_combine.Rmd
added analysis with cosine distance

df_main_analysis <- df #keep a copy of df in case exploratory analysis changes it
write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI.csv")
```

>>>>

df_main_analysis <- df #keep a copy of df in case exploratory analysis changes it
write.csv(df_main_analysis, "../../data/data_USCNVN_ENZHVI.csv", row.names = F)
write.csv(triads_omit, "../../data/triads_omit.csv", row.names = F)
```

### 2022-12-31 code/2_combine/2_combine_filler.Rmd
added analysis with cosine distance

```{r corpus filler just English, include = F}
df.corpus_filler <- read.csv("../../data/corpus/corpusEMV_filler.csv") %>%
  select(ends_with("_E") | ends_with("_M") | ends_with("_V")) %>%
  mutate(cue_id = cue_E)
```

```{r corpus - frequency, include = F}
#find triads_omit, used whenever analysis uses raw collocates 
corpus_E_omit <- df.corpus_filler %>% 
  filter(word1_match_frequency_E == 0 & word2_match_frequency_E == 0) # = 0 so no need to do this.
```

@@

```{r getting triads from the 3 languages, include = F}
#combine response and corpus data
df.filler_E <- df.resp_E %>%
  filter(stim_type == "filler",
         responses != "NA") %>%
  select(-variable_type, -trial_index, -trial_type, -stim_type) %>%
  mutate(language = "English", 
         country = "US")

@@

df.filler_E <- df.filler_E %>%
  mutate(responses_word1 = ifelse(responses == word1_E, 1, 0))

```

@@

df <- df %>%
  mutate(word1_match_frequency_prop_E = 
           word1_match_frequency_E / (word1_match_frequency_E + word2_match_frequency_E),
         word1_match_frequency_prop_M = 
           word1_match_frequency_M / (word1_match_frequency_M + word2_match_frequency_M),
         word1_match_frequency_prop_V = 
           word1_match_frequency_V / (word1_match_frequency_V + word2_match_frequency_V))

write.csv(df, "../../data/data_filler_USCNVN_ENZHVI.csv")
```

>>>>

```{r corpus filler just English, include = F}
df.corpus_filler <- read.csv("../../data/corpus/corpusEMV_filler.csv") %>%
  select(ends_with("_E") | ends_with("_M") | ends_with("_V")) %>%
  select(!(contains("cue_frequency") | contains("word1_frequency") | contains("word2_frequency"))) %>% # ignore base frequencies for now
  mutate(cue_id = cue_E)
```

```{r corpus - frequency, include = F}
#find triads_omit, used whenever analysis uses raw collocates 
triads_omit <- df.corpus_filler %>% 
  filter((word1_match_frequency_E == 0 & word2_match_frequency_E == 0) |
          #(word1_match_frequency_M == 0 & word2_match_frequency_M == 0) |
           (word1_match_frequency_V == 0 & word2_match_frequency_V == 0)) %>%
  pull(cue_id)
```

@@

```{r getting triads from the 3 languages}
#combine response and corpus data
df.filler_E <- df.resp_E %>%
  filter(stim_type == "filler",
         responses != "NA") %>%
  select(-variable_type, -trial_index, -trial_type, -stim_type) %>%
  mutate(language = "English", 
         country = "US")

@@

df.filler_E <- df.filler_E %>%
  mutate(responses_word1 = ifelse(responses == word1_E, 1, 0))
```

@@

df <- df %>%
  mutate(word1_match_frequency_prop_E = 
           word1_match_frequency_E / (word1_match_frequency_E + word2_match_frequency_E),
         word1_match_frequency_prop_M = 
           word1_match_frequency_M / (word1_match_frequency_M + word2_match_frequency_M),
         word1_match_frequency_prop_V = 
           word1_match_frequency_V / (word1_match_frequency_V + word2_match_frequency_V), 
         word1_match_cosine_prop_E = 
           word1_match_cosine_E / (word1_match_cosine_E + word2_match_cosine_E),
         word1_match_cosine_prop_M = 
           word1_match_cosine_M / (word1_match_cosine_M + word2_match_cosine_M),
         word1_match_cosine_prop_V = 
           word1_match_cosine_V / (word1_match_cosine_V + word2_match_cosine_V), 
         )

write.csv(df, "../../data/data_filler_USCNVN_ENZHVI.csv", row.names = F)
write.csv(triads_omit, "../../data/fillers_omit.csv", row.names = F)
```

### 2022-12-31 code/3_analysis/3_analysis_compare_freq_cosine.Rmd
added analysis with cosine distance

# Comparing between 2 models for VN responding
```{r US responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# Vietnamese 
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(near(theme_frequency_V, .Machine$double.eps) & 
                                  near(tax_frequency_V, .Machine$double.eps))), 
          family="binomial")
summary(fit.VI_VN)
fit.VI_VN.anova = Anova(fit.EN_US, type = 3)

@@

```
# Does adding country help with the model (compared to with just English co-occurrence)? 
```{r}
fit.language = glmer(responses_theme ~ theme_freq_prop_E + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(near(theme_frequency_E, .Machine$double.eps) & 
                                  near(tax_frequency_E, .Machine$double.eps))),

@@

fit.country_language = glmer(responses_theme ~ theme_freq_prop_E * country + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(near(theme_frequency_E, .Machine$double.eps) & 
                                  near(tax_frequency_E, .Machine$double.eps))),

@@

Adding country improves the model (thematic proportion of lexical co-occurrence, country, and their interaction were all significant predictors).

>>>>

# Comparing between 2 models for VN responding
```{r VN responding predicted by each corpus model raw co-occurrences, warning=FALSE}
# Vietnamese 
fit.VI_VN = glmer(responses_theme ~ theme_freq_prop_V + (1 | subject) + (1 | triad), 
          data = df %>% filter(country == "Vietnam", 
                               !(near(theme_frequency_V, .Machine$double.eps) & 
                                  near(tax_frequency_V, .Machine$double.eps))), 
          family="binomial")
summary(fit.VI_VN)
fit.VI_VN.anova = Anova(fit.EN_US, type = 3)

@@

# Does adding country help with the model (compared to with corresponding lexcial co-occurrence)? 
```{r}
df <- df %>%
  mutate(theme_freq_prop_corr_lang = case_when(
    country == "US" ~ theme_freq_prop_E,
    country == "China" ~ theme_freq_prop_M, 
    country == "Vietnam" ~ theme_freq_prop_V)) %>%
  mutate(theme_frequency_corr_lang = case_when(
    country == "US" ~ theme_frequency_E,
    country == "China" ~ theme_frequency_M, 
    country == "Vietnam" ~ theme_frequency_V)) %>%
  mutate(tax_frequency_corr_lang = case_when(
    country == "US" ~ tax_frequency_E,
    country == "China" ~ tax_frequency_M, 
    country == "Vietnam" ~ tax_frequency_V))

fit.language = glmer(responses_theme ~ theme_freq_prop_corr_lang + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(near(theme_frequency_corr_lang, .Machine$double.eps) & 
                                  near(tax_frequency_corr_lang, .Machine$double.eps))),

@@

fit.country_language = glmer(responses_theme ~ theme_freq_prop_corr_lang * country + (1 | subject) + (1 | triad), 
          data = df %>% filter(!(near(theme_frequency_corr_lang, .Machine$double.eps) & 
                                  near(tax_frequency_corr_lang, .Machine$double.eps))),

@@

Adding country improves the model. Only country and interaction between country and corresponding corpus's lexical co-occurrence were significant predictors. Corresponding corpus's lexical co-occurrence is no longer a significant predictor.
